---
title: "721_p1_jinalee"
author: "Jina Lee"
date: "October 4, 2015"
output: html_document
---

Attribute Selecition & Simplify column names
```{r}
tract.extracted<-read.csv("tract_extracted.csv")

# change column name of population: "Tot_Population_ACS_09_13" -> "Population"

var <-colnames(tract.extracted)
newColnames <- c("X", "GIDTR", "State", "State_name", "County", "County_name", "Tract", "Income", "Med_House_val", "ReturnRate", "pct_Males", "pct_Pop_5_17", "pct_Pop_18_24","pct_Pop_25_44", "pct_Pop_45_64", "pct_Pop_65plus", "pct_Hispanic", "pct_NH_White_alone", "pct_NH_Blk_alone", "pct_Not_HS_Grad",  "pct_College", "pct_Prs_Blw_Pov_Lev", "pct_Diff_HU_1yr_Ago", "pct_MrdCple_HHD", "pct_Female_No_HB", "pct_Sngl_Prns_HHD", "avg_Tot_Prns_in_HHD",  "pct_Rel_Under_6", "pct_Vacant_Units", "pct_Renter_Occp_HU", "pct_Single_Unit", "Population", "LAND_AREA", "density")

#colnames(tract.extracted)[grep("Tot_Population_ACS_09_13",colnames(tract.extracted))] <- "Population"
colnames(tract.extracted) <- newColnames
sapply(tract.extracted,mode)

attach(tract.extracted)

tract.extracted<-transform(tract.extracted,Income=as.numeric(Income)/1000)

attach(tract.extracted)

```

Data Preprocessing
```{r}
#races
tract.extracted$pct_Hispanic_f <- cut(pct_Hispanic, breaks = c(0,50,75,100))
tract.extracted$pct_NH_White_alone_f <- cut(pct_NH_White_alone, breaks = c(0,50,75,100))
tract.extracted$pct_NH_Blk_alone_f <- cut(pct_NH_Blk_alone, breaks = c(0,50,75,100))

var_races<-as.factor(c("pct_Hispanic_f","pct_NH_White_alone_f","pct_NH_Blk_alone_f"))

# by ages
tract.extracted$pct_Pop_5_17_f <- cut(pct_Pop_5_17, breaks = c(0,50,75,100))
tract.extracted$pct_Pop_18_24_f <- cut(pct_Pop_18_24, breaks = c(0,50,75,100))
tract.extracted$pct_Pop_25_44_f <- cut(pct_Pop_25_44, breaks = c(0,50,75,100))
tract.extracted$pct_Pop_45_64_f <- cut(pct_Pop_45_64, breaks = c(0,50,75,100))
tract.extracted$pct_Pop_65plus_f <- cut(pct_Pop_65plus, breaks = c(0,50,75,100))

# by single,married
tract.extracted$pct_MrdCple_HHD_f <- cut(pct_MrdCple_HHD, breaks = c(0,50,75,100))
tract.extracted$pct_Female_No_HB_f <- cut(pct_Female_No_HB, breaks = c(0,50,75,100))
tract.extracted$pct_Sngl_Prns_HHD_f <- cut(pct_Sngl_Prns_HHD, breaks = c(0,50,75,100))


# by education
tract.extracted$pct_Not_HS_Grad_f <- cut(pct_Not_HS_Grad, breaks = c(0,50,75,100))
tract.extracted$pct_College_f <- cut(pct_College, breaks = c(0,50,75,100))

# density
tract.extracted$density_f<-cut(density,c(quantile(density,na.rm=TRUE)))

Population_byState <- as.data.frame(tapply(tract.extracted$Population,State_name,sum, na.rm=TRUE))
LAND_AREA_byState<-as.data.frame(tapply(tract.extracted$LAND_AREA, State_name,sum, na.rm=TRUE))
density_byState <- as.data.frame(Population_byState/LAND_AREA_byState)
colnames(density_byState)<- "density_byState"
state<-rownames(density_byState)

density_byState_f <- cut(density_byState$density_byState, breaks=quantile(density_byState, na.rm=TRUE))

byState <- data.frame(state,Population_byState, LAND_AREA_byState, density_byState, density_byState_f)
colnames(byState)<- c("State","Population_byState","LAND_AREA_byState","density_byState", "density_byState_f")


attach(tract.extracted)
```

Mail Return Rate Summary
```{r}
summary(ReturnRate)
```


# Plot 0: Mail Return Rate Distribution
median will be added.
```{r}
library(ggplot2)
library(scales)
library(RColorBrewer)

#pdf("p0.pdf", useDingbats=F)
p0 <- ggplot(data=tract.extracted
             ,aes(x=ReturnRate)
             )+
  geom_density(stat='density', position='identity')+
  coord_cartesian()
 
p0 + geom_vline(xintercept = median(ReturnRate,na.rm=TRUE)
               , stat = "vline"
               , position = "identity"
               , color = 'red'
               , show_guide = FALSE)

 median(ReturnRate,na.rm=TRUE)

# dev.off()
```

# 1. Overall, by State
Descended Sorting a order of states by return rate
```{r}
rm(byState.median)
byState.median <-as.data.frame(tapply(ReturnRate,State_name, median, na.rm=TRUE))
colnames(byState.median)<- c("medReturnRate")
attach(byState.median)

byState.median<-byState.median[order(-medReturnRate),]
State_sorted<-rownames(byState.median)


```

## 1.1: Population by States

Population by States
!!! color by density will be added
```{r}
#pdf("p1_1.pdf")

p1.1 <- ggplot(data = byState
               , aes(x= factor(state, levels=State_sorted)
                     , y= Population_byState
                     , fill = factor(density_byState_f)
                     )
               )+
  geom_bar(stat="identity"
          , na.rm=TRUE)+
  coord_cartesian()+
  theme(axis.text.x = element_text(angle = 0, hjust = 1, size= rel(1)))+
  scale_fill_brewer()+
  coord_flip()+
  scale_y_reverse()

print(p1.1)


#dev.off()

#############################


```



## 1.2: Return Rate by States
setting data for a plot
```{r}
# pdf("p1_2.pdf")
p1.2<- ggplot(data=tract.extracted
            , aes(x=factor(State_name, levels=State_sorted)                                       , y=ReturnRate)
                  )

## creating box plot
bp <- p1.2+geom_boxplot(stat = "boxplot"
                , position = "dodge"
                , outlier.colour = "black"
                , outlier.shape = 16
                , outlier.size = 2
                , notch = FALSE
                , notchwidth = 0.5) +
  xlab("State")+
  ylab("Mail Return Rate (%)")+
  ylim(30,100)+
  ggtitle("Mail Return Rate by State")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


##add horizontal line of median return rate

bp+ geom_hline(yintercept = median(ReturnRate,na.rm=TRUE)
               , stat = "hline"
               , position = "identity"
               , color = 'red'
               , show_guide = FALSE)+
  coord_flip()
# dev.off()
```


# Correlation of Return Rate and other variables

function for drawing and save graphs of relationship between two variables
```{r}

drawGraph <- function(x_var, y_var, plotname){
  #pdf(paste(plotname,"_1.pdf"))
    p1<- qplot( x= x_var
                , y=y_var
                , geom='boxplot')
    p1<-p1+
      geom_hline(yintercept = median(y_var,na.rm=TRUE)
                 , stat = "hline"
                 , position = "identity"
                 , color = 'red'
                 , show_guide = FALSE
                 )
    p1<- p1+ labs(list(title = paste("Return Rate by",plotname)
                       , x = paste("Percentage of",plotname)
                       , y = "Mail Return Rate"
                       )
                  )
    
    print(p1)
  #dev.off()
  
  #pdf(paste(plotname,"_2.pdf"))
    p2 <- qplot(x = x_var
              , geom="histogram")
    p2<-p2 +
      scale_y_reverse()+
      labs(x = paste("Percentage of",plotname))
                
    print(p2)
  #dev.off()
    
return("completed")
}
```

##2. Income
```{r}

##na : null
medIncome.quant <- quantile(Income, na.rm=TRUE) #converted into (thousand) 
tract.extracted$IncomeQuant<-cut(Income, breaks = medIncome.quant)
attach(tract.extracted)

drawGraph(x_var=IncomeQuant,y_var=ReturnRate,"Income")
```



## 3. race vs returnRate

```{r}

#hispanic
drawGraph(x_var=pct_Hispanic_f,y_var=ReturnRate,"Hispanic")

#white
drawGraph(x_var=pct_NH_White_alone_f,y_var=ReturnRate,"White")

#black
drawGraph(x_var=pct_NH_Blk_alone_f,y_var=ReturnRate,"Black")

```


## 4. by Age
```{r}


# 1 pct_Pop_5_17

drawGraph(x_var=pct_Pop_5_17_f,y_var=ReturnRate,"5_17 years_old")


#2 pct_Pop_18_24
drawGraph(x_var=pct_Pop_18_24_f,y_var=ReturnRate,"18_24 years old")


#3 pct_Pop_25_44
drawGraph(x_var=pct_Pop_25_44_f,y_var=ReturnRate,"25_44 years old")


#4 pct_Pop_45_64
drawGraph(x_var=pct_Pop_45_64_f,y_var=ReturnRate,"45_64 years old")


#5 pct_Pop_65plus
drawGraph(x_var=pct_Pop_65plus_f,y_var=ReturnRate,"65plus years old")

```



##5. Single or Married

```{r}

#Married Couple
drawGraph(x_var=pct_MrdCple_HHD_f,y_var=ReturnRate,"Married Couple")


#Single Person
drawGraph(x_var=pct_Sngl_Prns_HHD_f,y_var=ReturnRate,"Single Person")

#Female No Husband
drawGraph(x_var=pct_Female_No_HB_f,y_var=ReturnRate,"Female without Husband")


```



##6.Education

```{r}

# No Highschool Graduate rate
drawGraph(x_var=pct_Not_HS_Grad_f,y_var=ReturnRate,"No Highschool Graduate")

# College percentage
drawGraph(x_var=pct_College_f,y_var=ReturnRate," College Graduate")

dev.off()
```

