---
title: "pr2_revise"
author: "Jina Lee"
date: "October 14, 2015"
output: html_document
---

environment/data setting
```{r}
library(shiny)
library(ggplot2)
library(rgdal)
library(plyr)

load("data/tract_noDuplicate.Rda")
load("data/state.Rda")

attach(tract)
attach(state)
```


ggplot local value issue.. doesn't recognize input values from ui
http://stackoverflow.com/questions/19531729/shiny-fill-value-not-passed-to-ggplot-correctly-in-shiny-server-error-object

```{r}
p <- p+
        #geom_point(alpha=.5,col=clr[i], aes(x=tract[,input$ages], y=tract$ReturnRate))+
      geom_point(alpha=.5,col=clr[i], aes(x=input$ages, y=ReturnRate))+  
      xlim(rng) #rng<-c(50,100)
      
      if(input$smooth==TRUE){
        p<- p+geom_smooth(col=clr[i], aes(x=tract[,input$ages],y=tract$ReturnRate))
      }
        
      print("xVars[i] before") 
      print(paste("i: ",i))
      print(xVars[i])
      print("after xVars[i]")
      
      print(p)
```



# corr function
```{r}
#plot<-p ; i=1+i
    draw.points <- function(x, y, plot, clr_i){
      plot <- plot+ geom_point(aes(x=tract[,x], y= tract[,y]), col = clr[clr_i], alpha = .2)
      plot
      return (plot)
    }
    
    draw.smooth <- function(x, y, plot, clr_i){
      p<- plot+geom_smooth(aes(x=tract[,x], y= tract[,y]), col = clr[clr_i], alpha = .2)
      return (p)
    }

```



# Row 1
```{r}

order.rRate<-order(state$ReturnRate)
order.pop<-order(state$population)

state_byRrate<-state[order.rRate,]
order<-state_byRrate$state_name

p1<- qplot(x= factor(tract$State_name, levels=order)
           , y= ReturnRate
           , data= tract
           )+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("State")+
  ylab("Return Rate(%)")

p1
summary(Tract)

```

reorder(x, ...) :a generic function. The "default" method treats its first argument as a categorical variable, and reorders its levels based on the values of a second variable, usually numeric.
```{r}
bymedian <- with(InsectSprays, reorder(spray, count, median))
boxplot(count ~ bymedian, data = InsectSprays,
        xlab = "Type of spray", ylab = "Insect count",
        main = "InsectSprays data", varwidth = TRUE,
        col = "lightgray")
```


# optoin 1. densed plot by color
```{r}

clr2 <- c("#1f78b4","#b2df8a","#33a02c","#fb9a99","#e31a1c","#fdbf6f","#ff7f00","#cab2d6",
         "#6a3d9a","#ffff99","#b15928")
clr<- c("#8dd3c7","#ffffb3","#bebada","#fb8072","#80b1d3","#fdb462","#b3de69","#fccde5","#d9d9d9")


ggplot(data=tract)+
  geom_point(aes(x=tract$pct_Pop_18_24,y=ReturnRate, col="18~24"), col=clr[1],alpha=.2)+
    geom_smooth(method=lm, aes(x=tract$pct_Pop_18_24,y=ReturnRate,col="18~24"),col=clr[1])+
  geom_point(aes(x=tract$pct_Pop_65plus,y=ReturnRate, col="65+"), col=clr[2],alpha=.2)+
    geom_smooth(method=lm, aes(x=tract$pct_Pop_65plus,y=ReturnRate, col="65+"),col=clr[2])+
  geom_point(aes(x=tract$pct_Pop_25_44,y=ReturnRate, col="25~44"), col="red",alpha=.2)+
    geom_smooth(method=lm, aes(x=tract$pct_Pop_25_44,y=ReturnRate, col="25~44"),col="red")


draw.points <- function(x, y, plot, clr_i){
  p <- plot+
    geom_point(aes(x=tract[,x], y= tract[,y])
               , col = clr[clr_i]
               , alpha = .2
               )+
    ylab("Return Rate(%)")+
    xlab("%")
  return (p)
}

draw.smooth <- function(x, y, plot, clr_i){
  p<- plot+
    geom_smooth(
      aes(x=tract[,x], y= tract[,y])
      , col = clr[clr_i]
      , alpha = .2
      )
  return (p)
}


p<- ggplot(data=tract)
p<-draw.points(x="pct_Pop_25_44", y="ReturnRate", plot=p, clr_i=1)
draw.smooth(x="pct_Pop_25_44", y="ReturnRate", plot=p, clr_i=1)

```



# option2. hexagonal bins aggregated plot

```{r}

library(hexbin)

hb<-hexbin(tract$Income, tract$ReturnRate)
plot(hb
     , xlab = "Income"
     , ylab = "Return Rate(%)"
     )


plot(hexbin(tract$pct_Pop_65plus, tract$ReturnRate)
     , xlab = "Income"
     , ylab = "Return Rate(%)"
     #, col = "red"
     )



```



# option3. hexagonal bins aggregated plot

```{r}

library(hexbin)

hb2<-hexbin(tract$pct_Pop_18_24, tract$ReturnRate)

p<- plot(hb2
         , type="n"
         ,main = "title"
         )

pushHexport(p$plot.vp)

col <- c("LinGray","BTC","LinOCS","heat.ob","magent","plinrain", terrain.colors, topo.colors, cm.colors)

library(RColorBrewer)

grid.hexagons(hb2
              #, style = "lattice"
              ,colramp= rainbow # 
              )

hb3<- hexbin(tract$pct_Pop_65plus, tract$ReturnRate)

grid.hexagons(hb3
              , style = "centroids"
              ,colramp=BTY
     )



```



## back up

### ui _ ages
```{r}
column(2
               , radioButtons("ages","Ages"
                                    ,c("18~24 years old"="pct_Pop_18_24"
                                       , "25~44 years old" = "pct_Pop_25_44"
                                       , "45~64 years old" = "pct_Pop_45_64"
                                       , "65+ years old" = "pct_Pop_65plus"
                                       )
                                    )
               )

```

